---
title: "Waterhemp Adaptation Trial"
author: "Nikola Arsenijevic"
date: "11/3/2020"
output:
  pdf_document: default
  html_document: default
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(drc)
library(ggplot2)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(plotly)
library(plotrix)
library(htmltools)
install.packages("usethis")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
red = read_csv("waterhemp.csv")

#red = read_csv("wh.csv")

#thered=read_csv("waterhemp.csv")
#str(red)
red$crop=factor(red$crop, levels = c("corn", "narrow", "wide", "fallow"), labels = c("Corn", "38 cm soybean", "76 cm soybean", "Fallow (Control)"))
#thered$crop=factor(thered$crop, levels = c("corn", "narrow", "wide", "fallow"), labels = c("Corn", "15-in soybean", "30-in soybean", "Fallow (Control)"))
```

## Roughly plotting the data, to view the overall look of it (height).
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(red, aes(x=date_tpl, y=height_cm, color=crop)) + geom_point() + theme_classic() +
  xlab("Transplant timing (1 - 5)") +
  ylab("Waterhemp height reduction (%)")
```






```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(red, aes(x=date_tpl, y=weight_g, color=crop)) + geom_point() + theme_classic() +
  xlab("Transplant timing (1 - 5)") +
  ylab("Waterhemp weight reduction (%)")
```



## Fitting the 'drm' model for waterhemp height reduction
```{r echo=TRUE, message=FALSE, warning=FALSE}
redukcija = drm(data=red, height_cm~date_tpl, crop, fct =W2.3(fixed = c(NA, NA,NA), names = c("slope", "upper", "ec50")))
summary(redukcija)

plot(redukcija, type="b", ylim = c(0,155))
```

## Checking if the fitted model is the best for the loaded data
```{r message=FALSE, warning=FALSE}
mselect(redukcija, list(l3(), l4(), W2.3(), W1.3(), W1.4(), W2.4(), LL.3(), LL.5(), W1.3(), W1.4(), W2.4()),
nested = F,
sorted = c("IC", "Res var", "Lack of fit", "no"),
linreg = F, icfct = AIC)
```


## Estimating ED50 and ED90 values for height reduction. Also, comparing the slopes of corn, 15in and 30in soybean.
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
ED(redukcija, c(50,90), type="absolute", interval = "delta")
compParm(redukcija, "slope", "-")
```


```{r message=FALSE, warning=FALSE, include=FALSE}
newdata <- expand.grid(date_tpl=exp(seq(log(161), log(211), length=211)))

newdata1 <- data.frame(crop =c("Corn"), newdata)
newdata2 <- data.frame(crop =c("38 cm soybean"), newdata)
newdata3 <- data.frame(crop =c("76 cm soybean"), newdata)
newdata4 <- data.frame(crop =c("Fallow (Control)"), newdata)
nd <- rbind(newdata1, newdata2, newdata3, newdata4)
str(nd)


pm <- predict(redukcija, newdata = nd, interval="confidence")

nd$p <- pm[,1]
nd$pmin <- pm[,2]
nd$pmax <- pm[,3]

red$date_tpl0 = red$date_tpl
red$date_tpl0[red$date_tpl0 == 0] <- 0.5
str(nd)
```

```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
ggplot(red, aes(x=date_tpl, y=height_cm, fill = crop))  +
  
  geom_ribbon(data=nd, aes(x=date_tpl, y=p, ymin=pmin, ymax=pmax), alpha=0.2) +
  geom_line(data=nd, aes(x=date_tpl, y=p)) + scale_fill_brewer(palette = "Set1") + 
  
  theme_classic() + ylim(-10, 165)+ xlim(161, 215) +
  
  labs(title = "Impact of corn and soybean canopy \n on waterhemp height \n") + 
  
  labs(x= "\n Transplant timing \n (increments in 10 days)", y = "Waterhemp height  (cm) \n") +
  theme(text = element_text(size=22),
  plot.background = element_rect(fill = "white"),
  axis.line = element_line(colour = "black", 
                           size = 0.1, linetype = "solid"),
  legend.position = "top", legend.title = element_blank(),
  plot.title = element_text(face = "bold", colour = "black", hjust = .5),
  aspect.ratio = 1/1,
  axis.text = element_text(face = "bold",color = "black")) + scale_x_discrete(name = "Day of the Year", limits=c(161, 171,181,191,201,211)) +
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(125.37, 78.37, 28.43, 11.31, 8), colour = "black", size=3.5, pch=15, alpha=0.5) +                    # corn 2019 
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(83.18, 36.53, 9.75, 1.06, 0.93), colour = "black", size=4, pch=16, alpha=0.5)+                     # 15in soybean
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(121.75, 74.41, 13.37, 3.37, 1.125), colour = "black", size=3.5, pch=17, alpha=0.5)+                  # 30in soybean
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(126, 138.75, 97.62, 69.5, 51.65), colour = "black", size=3.5, pch=18, alpha=0.5) +              # fallow
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(105.43, 91.56, 62.43, 32.81, 12.5, 10.75), colour = "red", size=3.5, pch=15, alpha=0.5) +   # corn 2020
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(138.68, 95.18, 13.18, 4.81, 0,0), colour = "red", size=3.5, pch=16, alpha=0.5)+             # 15in soybean
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(124, 149.12, 81.18, 9.5,0,0), colour = "red", size=3.5, pch=17, alpha=0.5)+              # 3in soybean
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(151.31, 128.37, 122.75, 121.62, 95.87, 68.31), colour = "red", size=4, pch=18, alpha=0.5, group=c("fallow"))  # fallow
  
```




## Fitting the 'drm' model for waterhemp weight.
```{r echo=TRUE, message=FALSE, warning=FALSE}
reduk = drm(data=red, weight_g ~ date_tpl, crop, fct =W1.3(fixed = c(NA,NA,NA), names = c("slope", "upper", "ec50")))
summary(reduk)




plot(reduk, ylim=c(0,500))


```



## Checking if the fitted model is the best for the loaded data (looking for the lowest IC value)
```{r message=FALSE, warning=FALSE}
mselect(reduk, list(l3(), l4(), W2.3(), W1.3(), W1.4(), W2.4(), LL.3(), LL.5(), W1.3(), W1.4(), W2.4(), baro5()),
nested = F,
sorted = c("IC", "Res var", "Lack of fit", "no"),
linreg = F, icfct = AIC)
```


## Estimating ED90 values for height reduction. Also, comparing the slopes of corn, 15in and 30in soybean.
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
ED(reduk, c(50,90), type="absolute", interval = "delta", display = T, curveid=CURVE)
compParm(reduk, "slope", "-")
```



```{r message=FALSE, warning=FALSE, include=FALSE}
newdataa <- expand.grid(date_tpl=exp(seq(log(161), log(211), length=211)))

newdataa1 <- data.frame(crop =c("Corn"), newdataa)
newdataa2 <- data.frame(crop =c("38 cm soybean"), newdataa)
newdataa3 <- data.frame(crop =c("76 cm soybean"), newdataa)
newdataa4 <- data.frame(crop =c("Fallow (Control)"), newdataa)
ndd <- rbind(newdataa1, newdataa2, newdataa3, newdataa4)


pmm <- predict(reduk, newdata = ndd, interval="confidence")

ndd$p <- pmm[,1]
ndd$pmin <- pmm[,2]
ndd$pmax <- pmm[,3]

red$date_tpl01 = red$date_tpl
red$date_tpl01[red$date_tpl01 == 0] <- 0.5
```


```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
ggplot(red, aes(x=date_tpl, y=weight_g, fill = crop)) + 
  
  geom_ribbon(data=ndd, aes(x=date_tpl, y=p, ymin=pmin, ymax=pmax), alpha=0.25) + 
  geom_line(data=ndd, aes(x=date_tpl, y=p)) + scale_fill_brewer(palette = "Set1") +   
  
  theme_classic() + ylim(-30,500) +
  
  labs(title = "Impact of corn and soybean canopy \n on waterhemp weight \n") + 
  
  labs(x= "\n Transplant timing \n (increments in 10 days)", y = "Waterhemp biomass (g) \n") +
  theme(text = element_text(size=22),
  plot.background = element_rect(fill = "white"),
  axis.line = element_line(colour = "black", 
                           size = 0.1, linetype = "solid"),
  legend.position = "top", legend.title = element_blank(),
  plot.title = element_text(face = "bold", colour = "black", hjust = .5),
  aspect.ratio = 1/1,
  axis.text = element_text(face = "bold",color = "black")) + scale_x_discrete(name = "Day of the Year", limits=c(161, 171,181,191,201,211)) + 
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(14.37, 0.78, 0.36, 11.31, 8), colour = "black", size=3, pch=15, alpha=0.5) +                    # corn 2019 
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(9.1, 0.42, 0.011, 0.01, 0.01), colour = "black", size=3, pch=16, alpha=0.5)+                     # 15in soybean
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(20.11, 8.26, 0.0275, 0.01, 0.01), colour = "black", size=3, pch=17, alpha=0.5)+                  # 30in soybean
  annotate("point", x = c(165, 175, 185, 195, 205), y=c(137.95, 79.66, 72.85, 70.92, 30.55), colour = "black", size=4, pch=18, alpha=0.5) +              # fallow
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(14.54, 6.21, 1.90, 0.44, 0.05, 0.05), colour = "red", size=3, pch=15, alpha=0.5) +   # corn 2020
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(26.31, 5.46, 0.08, 0.02, 0,0), colour = "red", size=3, pch=16, alpha=0.5)+             # 15in soybean
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(60.98, 29.51, 3.45, 0.04, 0,0), colour = "red", size=3, pch=17, alpha=0.5)+              # 3in soybean
  annotate("point", x = c(161, 171, 181, 192, 201, 211), y=c(470.1, 214, 194.16, 160.7, 79.07, 25.42), colour = "red", size=4, pch=18, alpha=0.5) # fallow
```


