---
title: "Waterhemp - MS - Height reduction by crop (tracking reduction by transplant timing, per each crop, respectively)"
author: "Nikola Arsenijevic"
date: "3/22/2021"
output: html_document
fig_width: 6 
fig_height: 4 
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(drc)
library(ggplot2)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(plotly)
library(plotrix)
library(htmltools)
library(ggthemes)
```

```{r include=FALSE}
data = read_csv("waterhemp-new-final.csv")
fig <- read_csv("ed50and90.csv")

data$crop=factor(data$crop, 
                 levels = c("corn", "narrow", "wide", "fallow"), 
                 labels = c("Corn", "38 cm soybean", "76 cm soybean", "Fallow (Control)"))
```

## Visualization of overall look of the data (waterhemp height reduction)
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data, 
       aes(x = tpl_1, 
           y=height_reduction_crop, 
           color=crop, size = height_cm)) + 
  geom_jitter(alpha = 0.5) + 
  theme_classic() +
  xlab("Transplanting period (days)") +
  ylab("Waterhemp height") +
  ylim(-25,110)
```

## Fitting the 'drm' model for waterhemp height reduction
```{r echo=TRUE, message=FALSE, warning=FALSE}
height_drm1 = drm(data=data, height_reduction_crop ~ tpl_1, crop, fct = W2.4(fixed = c(NA,0,100,NA), names = c("slope","lower", "upper", "ec50")))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
summary(height_drm1)
plot(height_drm1, type="b", log = "", ylim=c(0,100), legend = F, lty = 1:1, size=7, col=c("red", "blue", "forestgreen", "black"))
legend(1, 95, legend=c("Corn",
                       "38 cm soybean",
                       "76 cm soybean",
                       "Fallow (Control)"),
       col=c("red", "blue", "forestgreen", "black"), 
       lty=1:1, 
       cex=0.75,
       text.font=3, bg='lightblue')
```

```{r message=FALSE, warning=FALSE}
mselect(height_drm1, list(l3(), l4(), W1.3(), W2.3(), W1.4(), W1.4()),
nested = F,
sorted = c("IC", "Res var", "Lack of fit", "no"),
linreg = F, icfct = AIC)
```

## Comparing ED50 and ED90 values for height reduction. Also, comparing the slopes of corn, 38 cm and 76 cm soybean.
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
slope=compParm(height_drm1, "slope", "-")

options(scipen = 999, digits = 4)
EDcomp(height_drm1, c(50,50), type="absolute")
ed50=as.data.frame(EDcomp(height_drm1, c(50,50), type="absolute"))

options(scipen = 50, digits = 4)
ed90=as.data.frame(EDcomp(height_drm1, c(90,90), type="absolute"))

```


```{r}
# Comparing slopes
slope

# Comparing ED50
ed50

# Comparing ED90
ed90
```
## Extracting the estimated ed50 and ed90 values for narrow and wide soybeans, corn and fallow treatment.
```{r echo=FALSE}
eds <- ED(height_drm1, c(50,90), type="absolute", interval = "delta") %>%
  as_tibble() %>%
  mutate(trt = c("38 cm soybean:50",
                 "38 cm soybean:90",
                 "76 cm soybean:50",
                 "76 cm soybean:90",
                 "Corn:50",
                 "Corn:90",
                 "Fallow:50",
                 "Fallow:90"))# %>%
  #ggplot(aes(x=fct_reorder(trt, Estimate), y=Estimate, color=trt)) +
  #geom_errorbar(aes(ymin = Lower, ymax=Upper)) +
  #geom_point() + coord_flip()

print(eds)
```

## Plotting the estimated ed50 and ed90 values for crops.
```{r echo=FALSE, message=FALSE, warning=FALSE}
  ggplot(fig, aes(x=fct_reorder(Treatment, Estimate), y=Estimate, color=Treatment)) +
  
  geom_errorbar(aes(ymin = Lower, ymax=Upper), width = 0.1) +
  geom_point() + 
  
  coord_flip() + 
  
  facet_grid(~id) + 

  theme_clean() + 
  theme(text = element_text(size=22),
        axis.title = element_text(size = 18)) +
         
  
  labs(x='Treatment', y = "Days from first transplanting")
  
```

## Making a nicer and more complex figure
```{r message=FALSE, warning=FALSE, include=FALSE}
newdataa <- expand.grid(tpl_1=exp(seq(log(1), log(50), length=50)))

newdataa1 <- data.frame(crop =c("Corn"), newdataa)
newdataa2 <- data.frame(crop =c("38 cm soybean"), newdataa)
newdataa3 <- data.frame(crop =c("76 cm soybean"), newdataa)
newdataa4 <- data.frame(crop =c("Fallow (Control)"), newdataa)
ndd <- rbind(newdataa1, newdataa2, newdataa3, newdataa4)


pmm <- predict(height_drm1, newdata = ndd, interval="confidence")

ndd$p <- pmm[,1]
ndd$pmin <- pmm[,2]
ndd$pmax <- pmm[,3]

data$tpl_11 = data$tpl_1
data$tpl_11[data$tpl_11 == 0] <- 0.5
```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
height <- ggplot(data, aes(x=tpl_1, y=height_reduction_crop, fill = crop, color=crop)) + 
  
  #geom_ribbon(data=ndd, aes(x=tpl_1, y=p, ymin=pmin, ymax=pmax), alpha=0.25) + 
  geom_line(data=ndd, aes(x=tpl_1, y=p)) + scale_fill_brewer(palette = "Set1") +
  stat_summary(geom = "point", fun.y = "mean", size = 2) +
  geom_jitter(aes(size=height_cm), alpha=0.4, width = 3) +
  theme_clean() +
  ylim(-10,110) +
  
  labs(x = 'Days from first transplanting (mid June)',
       y = 'Waterhemp height reduction (%)')

height
```

